Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete

### 2015-10-16 main/LMCS.tex
More typo corrections

The correctness condition ensures that every proof net on a sequent encoding a 3-partition problem gives a solution that problem. If two jumps from a formula encoding a number $i$ connect to different formulae $K_j$ and $K_m$, a cycle is created immediately. Thus, the jumps from each $i$ must all connect to the same $K$, and the number of occurrences of $\bot$ and $\1$ in the encoding then ensures that when the formulae for $i_a$, $i_b$, and $i_c$, connect to one formulae $K$, their values sum to $k$, $i_a+i_b+i_c=k$.

@@

The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs. This problem is \capsabbrev{pspace}-complete, and remains so under various restrictions: inflow constraints can be fixed at the value 2, edge weights can be restricted to the value 1 and 2, the graphs can be required to be planar, and loops and double edges (edges connecting the same 2 vertices) can be prohibited, for example.

>>>>

The correctness condition ensures that every proof net on a sequent encoding a 3-partition problem gives a solution to that problem. If two jumps from a formula encoding a number $i$ connect to different formulae $K_j$ and $K_m$, a cycle is created immediately. Thus, the jumps from each $i$ must all connect to the same $K$, and the number of occurrences of $\bot$ and $\1$ in the encoding then ensures that when the formulae for $i_a$, $i_b$, and $i_c$, connect to one formulae $K$, their values sum to $k$, $i_a+i_b+i_c=k$.

@@

The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs. This problem is \capsabbrev{pspace}-complete, and remains so under various restrictions: inflow constraints can be fixed at the value 2, edge weights can be restricted to the value 1 and 2, the graphs can be required to be planar, and loops and double edges (edges connecting the same pair of vertices) can be prohibited, for example.
